How to obtain the redshift distribution from probabilistic redshift estimates

### 2019-05-17 research/paper/draft.tex
setting up some things for revising the paer

\usepackage{tikz}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{graphicx}
\graphicspath{{./}{./figures/}}
\bibliographystyle{apj}

@@

\newcommand{\myemail}{aimalz@nyu.edu}
\newcommand{\mathul}[1]{\underline{#1}}
\newcommand{\chippr}{CHIPPR}
\newcommand{\nz}{$n(z)$}
\newcommand{\pz}{photo-$z$}
\newcommand{\pzpdf}{photo-$z$ PDF}
\newcommand{\lsst}{\textsc{lsst}}

\newcommand{\aim}[1]{\textcolor{blue}{#1}}

@@

\begin{abstract}
A trustworthy estimate of the redshift distribution $n(z)$ is crucial for weak-lensing cosmology as we know it.
Spectroscopic redshifts for the dim and numerous galaxies of weak-lensing surveys are expected to be inaccessible, making photometric redshifts (photo-$z$s) the next-best alternative.
The nontrivial systematics affecting photo-$z$ estimation have motivated the weak-lensing community to favor photo-$z$ probability density functions (PDFs) as a more comprehensive alternative to photo-$z$ point estimates.
However, analytic methods for utilizing these new data products in cosmological inference are still evolving.
The ubiquitous methodology known as stacking produces a systematically biased estimator of $n(z)$ that worsens with decreasing signal-to-noise, the very regime where photo-$z$ PDFs are most necessary.
We introduce a mathematically rigorous probabilistic graphical model (PGM) of hierarchical inference of $n(z)$, which is provably the only self-consistent way to combine photo-$z$ PDFs to produce an estimator of $n(z)$.
The novel Cosmological Hierarchical Inference with Probabilistic Photometric Redshifts (CHIPPR) model yields a more accurate characterization of $n(z)$ by correctly propagating the redshift uncertainty information beyond the best-fit estimator produced by traditional procedures.
We conclude by propagating these effects to constraints in the space of cosmological parameters.
\end{abstract}

@@

\aim{Brief literature review:\\
Major data releases including \pzpdf s\\
The cosmology papers by those missions that stack PDFs\\
Recent papers simultaneously inferring \pzpdf s and \nz}

\aim{Q: What is the status quo?\\
A: The future of galaxy surveys is \pz s, and \pzpdf s rightfully replace \pz s; however, usage of \pzpdf s is limited.}

\aim{Q: Why should we question existing methods?\\
A: Stacking is bad and only looks like it works because of assumptions that don't hold when the data is as bad as we anticipate.  Cite pedantic doc?}

\begin{itemize}
	\item
	Q: How can we improve the effectiveness of using \pzpdf s in inference?\\
	A: Hierarchical inference is the only self-consistent way; see flow chart for outline of how it works in practice.
	\item
	Q: How does the result of \chippr compare to established estimators in terms of the accuracy of \nz ?\\
	A: \chippr\ yields the best possible \nz , conditional on the accuracy of the \pzpdf s used.
	\item
	Q: How does the result of \chippr compare to established estimators in terms of the precision on cosmological constraints?
\end{itemize}

\section{Methods}
\label{sec:methods}

\textcolor{blue}{Q: How can we improve the effectiveness of using \pzpdf s in inference?\\
A: Hierarchical inference is the only self-consistent way.}

\subsection{Model generalities}
\label{sec:model}

We begin by reframing the redshift distribution \nz\ from a probabilistic perspective.
Here we define a redshift distribution \nz\ as the normalized probability density
\begin{equation}
\label{eqn:nz}
\int_{-\infty}^{\infty}\ n(z)\ dz\ \equiv\ \frac{1}{J}\ \int_{-\infty}^{\infty}\ \sum_{j=1}^{J}\ \delta(z_{j},\ z)\ dz = 1
\end{equation}
of finding a galaxy $j$ in a catalog of $J$ galaxies having a redshift $z$.
We may without loss of generality impose a parametrization
\begin{equation}
\label{eqn:fz}
f_{\phi}(z)\ \equiv\ n(z)
\end{equation}
in terms of some parameter vector $\phi$.
We believe that galaxy redshifts are indeed drawn from \nz, making it a probability density over redshift; this fact can also be confirmed from dimensional analysis of Equation~\ref{eqn:nz}.
Therefore, it can be rewritten as
\begin{equation}
\label{eqn:pz}
z_{j}\ \sim\ \Pr(z \mid \phi)\ \equiv\ f_{\phi}(z),
\end{equation}
a probability density over redshift conditioned on the parameters defining \nz.
Note that $z_{j}$ does not depend on $z_{j'}$, a statement of the causal independence of galaxy redshifts from one another.

In addition to believing \nz\ is a PDF from which redshifts are drawn, we also believe that there is some PDF from which photometric data $d$, which may be any combination of fluxes, magnitudes, colors, and their observational errors, are drawn.
Such a PDF over data is a likelihood
\begin{equation}
\label{eqn:pzpdf}
d\ \sim\ \Pr(d \mid z)
\end{equation}
conditioned on redshift.
This assumption that the data are drawn from some function of the redshift forms the foundation upon which \pz\ estimation is based.
Note that galaxies may have different observational data $d$ despite sharing the same redshift and that the data $d_{j}$ of one galaxy is causally independent of the redshifts $z_{j'}$ and data $d_{j'}$ of other galaxies.

This description of the physical system corresponds to a forward model by which we actually believe photometry is generated:
\begin{enumerate}
	\item There exists a redshift distribution \nz\ with parameters $\phi$.
	\item Galaxy redshifts $\{z_{j}\}$ are independent draws from $\Pr(z 
\mid \phi)$.
	\item Galaxy photometry $d_{j}$ is drawn from the likelihoods $\Pr(d | 
z_{j})$.
\end{enumerate}
A forward model such as this corresponds to a probabilistic graphical model (PGM), represented by a directed acyclic graph (DAG) as in Figure~\ref{fig:pgm}.
\begin{figure}
	\begin{center}
		\includegraphics[width=0.25\textwidth]{fig/pgm.png}
		\caption{The PGM}
		\label{fig:pgm}
	\end{center}
\end{figure}
A DAG conveys the causal relationships between physical parameters and, like a Feynman diagram in the context of particle physics, is a shorthand for mathematical relationships between variables.

\subsection{Application to cosmology}
\label{sec:application}

The problem facing cosmologists is to determine the true parameters $\phi_{0}$ of \nz\ from observing the photometry $\{d_{j}\}$ of a large sample of galaxies $j$.
To self-consistently propagate the uncertainty in the redshifts, however, it is more appropriate to estimate the posterior $\Pr(\phi \mid \{d_{j}\})$ over all possible parameters $\phi$ (and thus potential redshift distributions \nz ) conditioned on all the observed data $\{d_{j}\}$ available in a generic catalog.

In order to use the DAG of Figure~\ref{fig:pgm} to derive an expression for $\Pr(\phi \mid \{d_{j}\})$ in terms of \pzpdf s, we must introduce two more concepts, confusingly named the implicit prior and the prior probability density.

When we constrain the redshift of a galaxy using its observed photometric data $d_{j}$, we are effectively estimating a posterior $\Pr(z \mid d_{j})$.
However, to do this, we must have a model for the general relationship between redshifts and photometry, whether empirical, as is the case for machine learning \pzpdf\ methods, or analytic, as is the case for template-based \pzpdf\ methods.
Such a relationship is defined in the space of probability density over redshift, so it must be able to be parameterized by the same functional form $f_{\phi}(z)$ as \nz .
It is thus natural to write it as $\Pr(z \mid \phi^{*})$, where $\phi^{*}$ is the parameters for this relationship under some generic \pzpdf\ method.
We call $\Pr(z \mid \phi^{*})$ the \textit{implicit prior}, as it is rarely explicitly known nor chosen by the researcher; for template-based methods where it can be chosen to be ``realistic,'' it may be appropriate to call it an \textit{interim prior}.
Because the implicit prior is unavoidable, the \pzpdf s reported by any method are really \textit{implicit-weighted posteriors} $\Pr(z \mid d, \phi^{*})$.

The prior probability density $\Pr(\phi)$ is a more familiar concept in astronomy; to progress, we will have to choose a prior probability density over all possible parameters $\phi$.
This prior need not be excessively proscriptive; for example, it may be chosen to enforce smoothness at physically motivated scales in redshift without imposing any particular region as over- or under-dense.

With these definitions, we obtain the desired expression for $\Pr(\phi \mid 
\{d_{j}\})$,
\begin{align}
\begin{split}
  \label{eqn:fullpost}
  \ln[\Pr(\phi \mid \{d_{j}\})] & \propto \ln[\Pr(\phi)] + \ln \left[\int dz 
\right.\\
  & \left. \exp \left[\sum_{j=1}^{J} \left(\ln[\Pr(z \mid d_{j}, \phi^{*})] 
\right. \right. \right.\\
  & \left. \left. \left. + \ln[\Pr(z \mid \phi)] - \ln[\Pr(z \mid \phi^{*})]\ 
\right)\ \right]\ \right] ,
\end{split}
\end{align}
which is the heart of \chippr.
The entire derivation of Equation~\ref{eqn:fullpost} is provided in Appendix~\ref{app:math}.

\subsection{Implementation}
\label{sec:implementation}

In this study, we compare the results of Equation~\ref{eqn:fullpost} to those of the two most common approaches to estimating \nz\ from a catalog of \pzpdf s: the distribution $n(z_{\mathrm{max}})$ of the redshifts at maximum posterior probability (i.e. the modes of the \pzpdf s), and the stacked estimator
\begin{align}
  \label{eqn:stacked}
  \hat{n}(z) &\equiv \frac{1}{J}\ \sum_{j=1}^{J}\ \Pr(z \mid d_{j}, \phi^{*}) .
\end{align}

We perform this comparison on mock data in the form of catalogs of emulated \pzpdf s generated via the forward model discussed above and presented in detail in Appendix~\ref{app:data}.
The mock data emulates the three sources of error of highest concern to the \pz\ community: intrinsic scatter, catastrophic outliers, and systematic bias.
Figure~\ref{fig:mega_scatter} illustrates these three effects individually at ten times the tolerance of the upcoming Large Synoptic Survey Telescope (LSST).
\begin{figure*}
	\begin{center}
		\includegraphics[width=0.3\textwidth]{fig/hivarsigmas_scatter.png}
    	\includegraphics[width=0.3\textwidth]{fig/uouthi_scatter.png}
    	\includegraphics[width=0.3\textwidth]{fig/neghivarbias_scatter.png}
		\caption{intrinsic scatter (left), uniform outliers (center), bias (right);
   		Not sure how best to broach the subject of nonuniform outliers and bias as model misspecification
    	}
		\label{fig:mega_scatter}
	\end{center}
\end{figure*}
Tests including all three effects at the tolerance levels of LSST are presented in Section~\ref{sec:results}.

\subsection{Limitations}
\label{sec:limitations}

Finally, we explicitly review the assumptions made by this approach.
\begin{itemize}
  \item prior $\Pr(\phi)$
  \item implicit prior $\phi^{*}$ known and shared among all PDFs
	\item \pzpdf s are accurate posteriors
	\end{itemize}

\section{Results}
\label{sec:results}

\textcolor{blue}{Q: How does the result of \chippr\ compare to established estimators in terms of the accuracy of $n(z)$?\\
A: \chippr\ yields the best possible $n(z)$, conditional on the accuracy of the photo-$z$ PDFs used.}

>>>>

\usepackage{tikz}
\usepackage{natbib}
\usepackage{amsmath}

@@

\newcommand{\todo}[3]{{\color{#2}\emph{#1}: #3}}
\newcommand{\aim}[1]{\todo{AIM}{red}{#1}}
\newcommand{\myemail}{aimalz@nyu.edu}
\newcommand{\mathul}[1]{\underline{#1}}
\newcommand{\Sect}[1]{Section~\ref{#1}}
\newcommand{\Eq}[1]{Equation~\ref{#1}}
\newcommand{\Fig}[1]{Figure~\ref{#1}}
\newcommand{\project}[1]{{\textsc{#1}}~}
\newcommand{\lsst}{\project{LSST}}
\newcommand{\desc}{\lsst-\project{DESC}}
\newcommand{\sdss}{\project{SDSS}}
\newcommand{\boss}{\project{BOSS}}
\newcommand{\des}{\project{DES}}
\newcommand{\Chippr}{\project{CHIPPR}}
\newcommand{\repo}[1]{{\texttt{#1}}~}
\newcommand{\qp}{\repo{qp}}
\newcommand{\chippr}{\repo{chippr}}
\newcommand{\cosmolike}{\repo{CosmoLike}}
\newcommand{\emcee}{\repo{emcee}}
\newcommand{\github}{\href{https://github.com}{GitHub}}
\newcommand{\python}{\textit{Python}}
\newcommand{\nz}{$n(z)$}
\newcommand{\data}{\ensuremath{\vec{d}}}
\newcommand{\like}{\mathscr{L}}
\newcommand{\pr}[1]{\ensuremath{\mathrm{p}(#1)}}
\newcommand{\expect}[1]{\left<#1\right>}
\newcommand{\normal}[2]{\mathcal{N} (#1, #2)}
\newcommand{\gvn}{\mid}% could use | or \vert
\newcommand{\integral}[2]{\ensuremath{\int\ #1\ \mathrm{d} #2}}
\newcommand{\sz}{spec-$z$~}
\newcommand{\Sz}{Spec-$z$~}
\newcommand{\pz}{photo-$z$~}
\newcommand{\Pz}{Photo-$z$~}
\newcommand{\pzpdf}{\pz PDF}
\newcommand{\Pzpdf}{\Pz PDF}
\newcommand{\zpdf}{redshift posterior}
\newcommand{\pzip}{\pz implicit posterior}
\newcommand{\Nz}{$N(z)$~}
\newcommand{\stack}{$\hat{N}(z)$~}
\newcommand{\ntot}{\ensuremath{N_{\mathrm{tot}}}}
\newcommand{\bvec}[1]{{\ensuremath{\boldsymbol{#1}}}}
\newcommand{\ndphi}{\bvec{\phi}}
\newcommand{\mmle}{marginalized maximum likelihood estimate}

@@

\begin{abstract}
A trustworthy estimate of the redshift distribution \nz\ is crucial for using 
galaxy catalogs to study cosmology via weak gravitational lensing and 
large-scale structure.
Spectroscopic redshifts for the dim and numerous galaxies of weak-lensing 
surveys are expected to be inaccessible, making photometric redshifts 
(photo-$z$s) the next-best alternative.
The nontrivial systematics affecting photo-$z$ estimation have motivated the 
weak-lensing community to favor photo-$z$ probability density functions (PDFs) 
as a more comprehensive alternative to photo-$z$ point estimates.
However, analytic methods for utilizing these new data products in cosmological 
inference are still evolving.
The ubiquitous methodology known as stacking produces a systematically biased 
estimator of $n(z)$ that worsens with decreasing signal-to-noise, the very 
regime where photo-$z$ PDFs are most necessary.
We introduce a mathematically rigorous probabilistic graphical model (PGM) of 
hierarchical inference of $n(z)$, which is provably the only self-consistent 
way to combine photo-$z$ PDFs to produce an estimator of $n(z)$.
The novel Cosmological Hierarchical Inference with Probabilistic Photometric 
Redshifts (\Chippr) model yields a more accurate characterization of $n(z)$ by 
correctly propagating the redshift uncertainty information beyond the best-fit 
estimator produced by traditional procedures.
We conclude by propagating these effects to constraints in the space of 
cosmological parameters.
\end{abstract}

@@

\aim{TODO: Pull in content from global intro to thesis.}

Though their potential to improve estimates of physical parameters is 
tremendous, \pzpdf s have been applied only to a limited extent.  
They have been used to form selection criteria of samples from galaxy surveys 
without propagation 
through the calculations of physical parameters 
\citep{VanBreukelen2009,Viironen2015}.  
Probability cuts on Bayesian quantities are not uncommon \citep{Leung2015, 
DiPompeo2015a}, but that procedure does not fully take advantage of all 
information contained in a probability distribution for parameter inference.

Despite the growing prevalence of \pzpdf\ production, no implementation of 
inference using \pzpdf s has yet been presented with a mathematically 
consistent methodology.  
I present and validate a hierarchical Bayesian technique for the use of \pzpdf\ 
in inference of arbitrary statistics relevant to cosmology, large-scale 
structure, and galaxy evolution.  
For simplicity, we consider only one-point statistics, though future work will 
extend this methodology to higher-order statistics.

The \textit{redshift distribution function \Nz}, or, almost interchangably, its 
normalized cousin the \textit{redshift density function \nz}, serves as an 
ideal statistic upon which to demonstrate this novel approach.  
\Nz\ is necessary for calculations of two-point correlation functions of weak 
gravitational lensing and counting statistics that are used to probe dark 
energy \citep{Masters2015}.  
The observed \Nz\ also been used to validate survey selection functions 
usnfenjed in generation of realistic, multi-purpose mock catalogs 
\citep{Norberg2002}.  
Additionally, \Nz\ has been the subject of inference using \pzpdf s before 
\citep{sheldon_photometric_2012, Hildebrandt2012, Kelly2014, Benjamin2013, 
bonnett_using_2015, Viironen2015, Asorey2016, leistedt_hierarchical_2016}, so 
comparisons to the literature may easily be made.

The prevailing way to estimate \nz\ for a sample of $\ntot$ galaxies $i$ is to 
``stack'' \pzpdf s according to Equation~\ref{intro:eq:eqn:stack}.
The stacked estimator of the redshift density function is effectively an 
average of the \pzpdf\ catalog and, as I will show in this paper, not in 
general mathematically valid.
Stacking is nonetheless considered the preferred method for obtaining \Nz\ from 
a \pzpdf\ catalog \citep{sheldon_photometric_2012, Kelly2014, Benjamin2013, 
bonnett_using_2015, Viironen2015, Asorey2016}.  
However, it must be noted here that Equation~\ref{intro:eq:eqn:stack} is not in 
general mathematically valid.  
(See \citet{Hogg2012} for a complete discussion.)

I aim to develop a clear methodology guiding the use of \pzpdf s in inference 
so they may be utilized effectively by the cosmology community.
Though others have approached the problem before 
\citep{leistedt_hierarchical_2016}, the method presented here differs in that 
it makes use of any existing catalog of \pzpdf s, rather than requiring a 
simultaneous derivation of the \pzpdf s and the redshift distribution, making 
it preferable to ongoing surveys that may be resistant to restructuring their 
analysis pipelines.

In Section~\ref{sec:meth}, I present the \Chippr\ model and \chippr\ 
implementation for characterizing the full posterior probability landscape of 
\Nz\ using \pzpdf s. 
In Section~\ref{sec:alldata}, I describe the experimental design for testing 
the fully probabilistic approach to mock and real datasets, the results of 
which are found in Section~\ref{sec:results}.
In Section~\ref{sec:results}, I stress-test the \Chippr\ model against stacking 
and its other competitors in the context of cosmology.

\section{Method}
\label{sec:meth}

Consider a survey of $J$ galaxies $j$, each with photometric data $\data_{j}$; 
thus the entire survey over some solid angle produces the ensemble of 
photometric magnitudes (or colors) and their associated observational errors 
$\{\data_{j}\}$.  
Each galaxy $j$ has a redshift $z_{j}$ that we would like to learn; redshift is 
a parameter in this case.  
The distribution of the ensemble of redshifts $\{z_{j}\}$ may be described by 
the hyperparameters defining the redshift distribution function \nz\ that we 
would like to quantify.  
This situation may be considered to be a probabilistic generative model, 
illustrated by the directed acyclic graph of \Fig{fig:pgm}.

The redshift distribution function \nz\ is the number of galaxies per unit 
redshift, effectively defining the evolution in the number of galaxies 
\citep{Menard2013}.  
In the following sections, I present and compare methods for estimating \nz\ 
from \pzpdf s.  
\Sect{sec:prob} contains the mathematical derivation of a probabilistic model 
for $n(z)$ dependent on photo-$z$ probability distribution functions, and 
\Sect{sec:sheldon} contrasts the probabilistic model with alternative methods.

\subsection{Forward Model}
\label{sec:forward}

We begin by reframing the redshift distribution \nz\ from a probabilistic 
perspective.
Here we define a redshift density \nz\ as the normalized probability density
\begin{equation}
\label{eqn:nz}
\int_{-\infty}^{\infty}\ n(z)\ dz\ \equiv\ \frac{1}{J}\ 
\int_{-\infty}^{\infty}\ \sum_{j=1}^{J}\ \delta(z_{j},\ z)\ dz = 1
\end{equation}
of finding a galaxy $j$ in a catalog of $J$ galaxies having a redshift $z$.
We believe that galaxy redshifts are indeed drawn from \nz, making it a 
probability density over redshift; this fact can also be confirmed by 
dimensional analysis of \Eq{eqn:nz}, as suggested in \citet{Hogg2012}.

We may without loss of generality impose a parameterization
\begin{equation}
\label{eqn:fz}
f(z; \ndphi)\ \equiv\ n(z)
\end{equation}
in terms of some parameter vector $\ndphi$.
At this point, the parameter vector is quite general and may represent 
coefficients in a high-order polynomial as a function of redshift, a set of 
means and variances defining Gaussians that sum to the desired distribution, a 
set of histogram heights that describe a binned version of the redshift 
distribution function, etc.
Upon doing so, we may rewrite \Eq{eqn:fz} as 
\begin{equation}
\label{eqn:pz}
z_{j}\ \sim\ \pr{z \gvn \ndphi}\ \equiv\ f(z; \ndphi),
\end{equation}
a probability density over redshift conditioned on the parameters $\ndphi$ 
specifying \nz.
Note that $z_{j}$ does not depend on the redshift $z_{j'}$ of some other galaxy 
$j' \neq j$, a statement of the causal independence of galaxy redshifts from 
one another.

In addition to believing \nz\ is a PDF from which redshifts are drawn, we also 
believe that there is some higher dimensional probability space $\pr{z, \data}$ 
of redshift and photometric data vectors $\data$, which may be any combination 
of fluxes, magnitudes, colors, and their observational errors.
In that sense \nz\ is equivalent to an integral
\begin{equation}
\label{eqn:integral}
n(z)\ =\ \integral{\pr{z, \data}}{\data}
\end{equation}
over the dimension of data in that joint probability space.
Note that galaxies may have different observational data despite sharing the 
same redshift, and that galaxies at different redshifts may have identical 
photometry; the space $\pr{z, \data}$ need not be one-to-one.
We assume a stronger version of statistical independence here, that draws 
$(z_{j}, \data_{j})$ are independent of draws $(z_{j'}, \data_{j'})$ in this 
space; the data and redshift of each galaxy are independent of those of other 
galaxies.

However, this problem has additional causal structure that we can acknowledge.
The photometry results from the redshifts, not the other way around.
This is the fundamental assumption upon which \pz\ estimation is based.
The forward model corresponds to first drawing redshifts according to 
\Eq{eqn:pz} and then drawing data from the likelihood
\begin{equation}
\label{eqn:pzpdf}
\data_{j}\ \sim\ \pr{\data \gvn z_{j}}
\end{equation}
of photometry conditioned on redshift, illustrated in 
Figure~\ref{intro:fig:fig:pedagogical_scatter}.

This description of the physical system corresponds to a forward model by which 
we actually believe photometry is generated:
\begin{enumerate}
	\item There exists a redshift distribution \nz\ with parameters 
$\ndphi$.
	\item Galaxy redshifts $\{z_{j}\}$ are independent draws from $\pr{z 
\gvn \ndphi}$.
	\item Galaxy photometry $\data_{j}$ is drawn from the likelihoods 
$\pr{\data_{j} \gvn z}$.
\end{enumerate}

\subsection{Probabilistic Model}
\label{sec:prob}

A forward model such as that of \Sect{sec:forward} corresponds to a 
probabilistic graphical model (PGM), represented by a directed acyclic graph 
(DAG) as in \Fig{fig:pgm}.
A DAG conveys the causal relationships between physical parameters and, like a 
Feynman diagram in the context of particle physics, is a shorthand for 
mathematical relationships between variables.
The photometric data $\data_{j}$ of a galaxy is drawn from some function of its 
redshift $z_{j}$, independent of other galaxies' data and redshift.
Both data and redshift are random variables, but data is the one that we 
observe and redshift is not directly observable.
In this problem, we don't care about further constraining the redshifts of 
individual galaxies, only the redshift distribution, so we consider redshift to 
be a \textit{latent variable}.
Because the parameters $\ndphi$ that we seek are causally separated from the 
data by the latent variable of redshift, we call them \textit{hyperparameters}.

\begin{figure}
	\begin{center}
		\includegraphics[width=0.2\textwidth]{figures/chippr/pgm.png}
		\caption{The directed acyclic graph of the CHIPPR model, where 
circles indicate random variables and arrows indicate causal relationships.
			The redshift distribution function parameterized by 
hyperparameters $\ndphi$ exists independent of the survey of $J$ galaxies, 
indicated as a box.  
			The redshifts $\{z_{j}\}$ of all galaxies in the survey 
are latent variables independently drawn from the redshift distribution, which 
is a function of $\ndphi$. 
			The photometric data $\data_{j}$ for each galaxy is 
drawn from a function of its redshift $z_{j}$ and observed, indicated by a 
shaded circle.}
		\label{fig:pgm}
	\end{center}
\end{figure}

The problem facing cosmologists is to determine the true value of $\ndphi$ from 
observing the photometry $\{\data_{j}\}$ of a large sample of $J$ galaxies $j$.
To self-consistently propagate the uncertainty in the redshifts, however, it is 
more appropriate to estimate the posterior $\pr{\ndphi \gvn \{\data_{j}\}}$ 
over all possible values of $\ndphi$ conditioned on all the observed data 
$\{\data_{j}\}$ available in a generic catalog.
In order to use the DAG of \Fig{fig:pgm} to derive an expression for 
$\pr{\ndphi \gvn \{\data_{j}\}}$ in terms of \pzpdf s, we must introduce two 
more concepts, confusingly named the implicit prior and the prior probability 
density.

When we constrain the redshift of a galaxy using its observed photometric data 
$\data_{j}$, we are effectively estimating a posterior $\pr{z \gvn \data_{j}}$.
However, to do this, we must have a model for the general relationship between 
redshifts and photometry, whether empirical, as is the case for machine 
learning \pzpdf\ methods, or analytic, as is the case for template-based 
\pzpdf\ methods.
Such a relationship is defined in the space of probability density over 
redshift, so it must be able to be parameterized by the same functional form 
$f(z; \ndphi)$ as \nz .
It is thus natural to write it as $\pr{z \gvn \ndphi^{*}}$, where $\ndphi^{*}$ 
is the parameters for this relationship under some generic \pzpdf\ method.
We call $\pr{z \gvn \ndphi^{*}}$ the \textit{implicit prior}, as it is rarely 
explicitly known nor chosen by the researcher; for template-based methods where 
it can be chosen to be ``realistic,'' it may be appropriate to call it an 
\textit{interim prior}.
Because the implicit prior is unavoidable, the \pzpdf s reported by any method 
are really \textit{implicit-weighted posteriors} $\pr{z \gvn \data, 
\ndphi^{*}}$.

The implicit prior $\ndphi^{*}$ may be thought of as an initial guess for the 
parameters contained in $\ndphi$, inspired by the generative model for 
photometry from the redshift distribution functions and including some 
parameters defining intrinsic galaxy spectra and instrumental effects. 
(See \citealt{benitez_bayesian_2000} for more detail.)  
For statistical purposes, we would like any interim prior to be uninformative, 
but this is rarely achievable.  
In the case of estimating \nz\ photometrically, it is common to use 
$\ndphi^{*}$ corresponding to \nz\ derived from some different, 
spectroscopically confirmed sample or from a cosmological simulation.

The prior probability density $\pr{\ndphi}$ is a more familiar concept in 
astronomy; to progress, we will have to choose a prior probability density over 
all possible parameters $\ndphi$.
This prior need not be excessively proscriptive; for example, it may be chosen 
to enforce smoothness at physically motivated scales in redshift without 
imposing any particular region as over- or under-dense.

With these definitions, we obtain the desired expression for $\pr{\ndphi \gvn 
\{\data_{j}\}}$,
\begin{align}
\begin{split}
\label{eqn:fullpost}
\pr{\ndphi \gvn \{\data_{j}\}} & \propto 
\pr{\ndphi}\left[\integral{\prod_{j=1}^{J} \left(\pr{z \gvn \data_{j}, 
\ndphi^{*}}\pr{z \gvn \ndphi}(\pr{z \gvn \ndphi^{*}})^{-1}\right)}{z}\right] ,
\end{split}
\end{align}
the heart of \Chippr.
The derivation is provided below in \Sect{app:math}.

\subsubsection{Derivation}
\label{app:math}

In this paper, we work exclusively with log-probabilities.  
What we wish to estimate is then the full log-posterior probability 
distribution (hereafter the full log-posterior) of the hyperparameters $\ndphi$ 
given the catalog of photometry $\{\data_{j}\}$.

By Bayes' Rule, the full log-posterior
\begin{equation}
\label{eqn:basicbayes}
\ln[\pr{\ndphi \gvn \{\data_{j}\}}] = \ln[\pr{\{\data_{j}\} \gvn \ndphi}] + 
\ln[\pr{\ndphi}] - \ln[\pr{\{\data_{j}\}}]
\end{equation}
may be expressed in terms of the full log-likelihood probability distribution 
(hereafter the full log-likelihood) $\ln[\pr{\{\data_{j}\} \gvn \ndphi}]$ by 
way of a hyperprior log-probability distribution (hereafter the hyperprior) 
$\ln[\pr{\ndphi}]$ over the hyperparameters and the log-evidence probability of 
the data $\ln[\pr{\{\data_{j}\}}]$.
However, the evidence is rarely known, so we probe the full log-posterior 
modulo an unknown constant of proportionality.

The full log-likelihood may be expanded in terms of a marginalization over the 
redshifts as parameters, as in 
\begin{equation}
\label{eqn:marginalize}
\ln[\pr{\{\data_{j}\} \gvn \ndphi}] = \ln\left[\integral{\pr{\{\data_{j}\} \gvn 
\{z_{j}\}} \pr{\{z_{j}\} \gvn \ndphi}}{\{z_{j}\}}\right].
\end{equation}

We shall make two assumptions of independence in order to make the problem 
tractable; their limitations are be discussed below.  
First, we take $\ln[\pr{\{\data_{j}\} \gvn \{z_{j}\}}]$ to be the sum of $J$ 
individual log-likelihood distribution functions $\ln[\pr{\data_{j} \gvn 
z_{j}}]$, as in 
\begin{equation}
\label{eqn:indiedat}
\ln[\pr{\{\data_{j}\} \gvn \{z_{j}\}}] = \sum_{j=1}^{J}\ \ln[\pr{\data_{j} \gvn 
z_{j}}],
\end{equation}
a result of the definition of probabilistic independence encoded by the box in 
\Fig{fig:pgm}.
Second, we shall assume the true redshifts $\{z_{j}\}$ are $J$ independent 
draws from the true $\pr{z \gvn \ndphi}$.  
Additionally, $J$ itself is a Poisson random variable.  
The combination of these assumptions is given by 
\begin{equation}
\label{eqn:indie}
\ln[\pr{\{z_{j}\} \gvn \ndphi}] = -\integral{f(z; \ndphi)}{z} + \sum_{j=1}^{J}\ 
\ln[\pr{z_{j} \gvn \ndphi}].
\end{equation}
The derivation differs when $J$ is not known, say, when we want to learn about 
a distribution in nature rather than a distribution specific to data in hand, 
but for a photometric galaxy catalog where the desired quantity is $n(z)$ for 
the galaxies entering a larger cosmology calculation, it is a fixed quantity.
A detailed discussion of this matter may be found in 
\citet{Foreman-Mackey2014}.  
Applying Bayes' Rule, we may combine terms to obtain 
\begin{equation}
\label{eqn:posterior}
\ln[\pr{\ndphi \gvn \{\data_{j}\}}] \propto \ln[\pr{\ndphi}] - \integral{f(z; 
\ndphi)}{z} + \sum_{j=1}^{J}\ln\left[\integral{\pr{\data_{j} \gvn z} \pr{z \gvn 
\ndphi}}{z}\right].
\end{equation}

Since we only have access to implicit \pz\ posteriors, we must be able to write 
the full log-posterior in terms of implicit \pz\ log-posteriors rather than the 
log-likelihoods of \Eq{eqn:posterior}.
To do so, we will need an explicit statement of this implicit prior 
$\ndphi^{*}$ for whatever method is chosen to produce the implicit \pz\ 
posteriors.

To perform the necessary transformation from likelihoods to posteriors, we 
follow the reasoning of \citet{Foreman-Mackey2014}.  
Let us consider the probability of the parameters conditioned on the data and 
an interim prior and rewrite the problematic likelihood of \Eq{eqn:posterior} 
as 
\begin{equation}
\label{eqn:trick}
\ln[\pr{\data_{j} \gvn z}] = \ln[\pr{\data_{j} \gvn z}] + \ln[\pr{z \gvn 
\data_{j}, \ndphi^{*}}] - \ln[\pr{z \gvn \data_{j}, \ndphi^{*}}].
\end{equation}

Once the implicit prior $\ndphi^{*}$ is explicitly introduced, we may expand 
the last term in \Eq{eqn:trick} according to Bayes' Rule to get 
\begin{equation}
\label{eqn:expand}
\ln[\pr{\data_{j} \gvn z}] = \ln[\pr{\data_{j} \gvn z}] + \ln[\pr{z \gvn 
\data_{j}, \ndphi^{*}}] + \ln[\pr{\data_{j} \gvn \ndphi^{*}}] - \ln[\pr{z \gvn 
\ndphi^{*}}] - \ln[\pr{\data_{j} \gvn z, \ndphi^{*}}].
\end{equation}
Because there is no direct dependence of the data upon the hyperparameters, we 
may again expand the term $\ln[\pr{\data_{j} \gvn z, \ndphi^{*}}]$ to obtain 
\begin{equation}
\label{eqn:indterm}
\ln[\pr{\vec{d}_{j} \gvn z}] = \ln[\pr{\data_{j} \gvn z}] + \ln[\pr{z \gvn 
\data_{j}, \ndphi^{*}}] + \ln[\pr{\data_{j} \gvn \ndphi^{*}}] - \ln[\pr{z \gvn 
\ndphi^{*}}] - \ln[\pr{\data_{j} \gvn z}] - \ln[\pr{\data_{j} \gvn \ndphi^{*}}].
\end{equation}
Canceling the undesirable terms for the inaccessible likelihood 
$\ln[\pr{\data_{j} \gvn z}]$ and trivial $\ln[\pr{\data_{j} \gvn \ndphi^{*}}]$ 
yields
\begin{equation}
\label{eqn:cancel}
\ln[\pr{\data_{j} \gvn z}] = \ln[\pr{z \gvn \data_{j}, \ndphi^{*}}]  - 
\ln[\pr{z \gvn \ndphi^{*}}].
\end{equation}
We put this all together to get the full log-posterior probability distribution 
of 
\begin{equation}
\label{eqn:final}
\ln[\pr{\ndphi \gvn \{\data_{j}\}}] \propto \ln[\pr{\ndphi}] + \ln 
\left[\integral{\exp \left[\sum_{j=1}^{J} \left(\ln[\pr{z \gvn \data_{j}, 
\ndphi^{*}}] + \ln[\pr{z \gvn \ndphi}] - \ln[\pr{z \gvn 
\ndphi^{*}}]\right)\right]}{z}\right] ,
\end{equation}
